---
title: "PUSH data correlation models"
format: pdf
editor: visual
author: 
  - Josie Peterburs
  - Nora Reinhardt
  - Gregory J. Matthews
---

# Introduction

The main goals of this exploratory analysis are to:

1.  Create a single data set that merges daily data with individual survey level data.
2.  Examine bivariate correlations between the identified sleep variables (e.g. average sleep time, etc.), the covariates (e.g. age, sex, etc.), and the environmental variables (COI index, P_COHESION, etc.).
3. Create models for dependent variables of interest with independent variables that represent neighborhood factors, family factors, and sleep environment characteristics.

```{r message = FALSE, warning=FALSE}
library(corrplot)
library(tidyverse)
library(lme4)
library(easystats)
library(lubridate)

# push_wide <- read_csv("./data/PUSH_actigraph_geo_wide_8.7.25.csv")
# push_long <- read_csv("./data/PUSH_long_geo.csv")
push_wide <- read_csv("PUSH_actigraph_geo_wide_8.7.25.csv")
push_long <- read_csv("PUSH_long_geo.csv")
```

# Merging long and wide data sets

For the PUSH data, there is a wide dataset with all the survey information for the participants of the study. The long dataset has day-by-day data for metrics from each night of sleep for the participants. These datasets were merged into a single dataset. The merged file is named "PUSH_Sleep_merged.csv". This file contained 204 rows and 1179 columns. There are 29 unique participant IDs all of whom have either 6, 7, or 8 measured days with the majority (20 out of 29) having 7 days measured.

```{r}
# Perform a left join
all <- left_join(push_long, push_wide, by = "ParticipantID")
dim(all)
all %>% group_by(ParticipantID) %>% summarize(days = n()) 

all %>% group_by(ParticipantID) %>% summarize(days = n()) %>% ungroup() %>% group_by(days) %>% summarize(n = n())

#Output all 
#write.csv(all, file = "/Users/gregorymatthews/Dropbox/PUSH-Sleep_git/data/PUSH_Sleep_merged.csv", row.names = FALSE)
```

# Exploratory Data Analysis

We began by observing the distribution of the independent variables of interest (dependent variable distributions are observed with their models below).

```{r}
vars <- all %>% select(ParticipantID, StudyDay, C_ACTI_Date,
                         # dependent vars
                         C_ACTI_Duration, 
                         C_ACTI_WT_DEC, 
                         C_ACTI_SOL, 
                         C_ACTI_SleepOnsetTime_TRM, 
                         C_ACTI_Efficiency, 
                         C_ACTI_Waso, 
                         C_ACTI_SleepTime_sd, 
                         C_ACTI_WakeTime_sd, 
                         C_ACTI_SleepTime_sd, 
                         # covariates
                         c_demo_8_v2, 
                         c_demo_6_v2, 
                         C_DD_PM_DayType,
                         #fixed effects
                         geo_COI_ED_3.0,
                         geo_COI_HE_3.0,
                         geo_COI_SE_3.0,
                         P_COHESION,
                         C_MESA_FT,
                         C_MESA_ES,
                         C_CHAOS,
                         c_se_12_v2,
                         c_se_8_v2,
                         c_se_11_v2) %>% 
  mutate(c_demo_8_v2 = as.factor(c_demo_8_v2),
         C_DD_PM_DayType = as.factor(C_DD_PM_DayType),
         c_se_12_v2 = as.factor(c_se_12_v2),
         c_se_8_v2 = as.factor(c_se_8_v2),
         c_se_11_v2 = as.factor(c_se_11_v2))
```

### Covariates

Because the datasets are merged, each row represents a recorded study day. The covariates, which are the same for an individual throughout the study, are not a count of the individuals, but rather a count of the number of study days.

Looking at the covariates, there are more study days recorded for females (139) than for males (65).

For grade in school, there are 49 recorded days for 8th graders, 55 for 9th graders, 50 for 10th graders, 21 for 11th graders, and 7 for 12th graders (likely one individual). There are also 8 observations with "7" as the level for this variable, which is not a valid level in the data dictionary. This individual is 13 years old, which is likely an 8th grader. The levels were renamed to match the grade (1 turns into 8 to indicate 8th grade, 2 into 9, etc.).

More study days were recorded in the summer (86) than during the academic school year (76).

We also created a variable to indicate whether the day was a Friday or Saturday night (called weekend).

```{r}
# c_demo_8_v2 -- Biological Sex
# MALE (1), FEMALE (2), DON’T KNOW (3), PREFER NOT TO ANSWER (4)
table(vars$c_demo_8_v2, useNA = "always")

# c_demo_6_v2 -- Grade in School
# 8th (1), 9th (2), 10th (3), 11th (4), 12th (5)
table(vars$c_demo_6_v2, useNA = "always")
all %>% filter(c_demo_6_v2 == 7) %>% select(c_demo_6_v2, c_demo_2_v2)

model <- vars %>% mutate(c_demo_6_v2 = case_when(
  c_demo_6_v2 == 1 ~ 8,
  c_demo_6_v2 == 2 ~ 9,
  c_demo_6_v2 == 3 ~ 10,
  c_demo_6_v2 == 4 ~ 11,
  c_demo_6_v2 == 5 ~ 12,
  c_demo_6_v2 == 7 ~ 8))
table(model$c_demo_6_v2, useNA = "always")

# C_DD_PM_DayType -- School or Summer
# Summer (0), Academic School Year (1)
table(model$C_DD_PM_DayType)

# add weekend variable
  # weekend = Friday or Saturday night
models <- model %>% mutate(weekday = wday(models$C_ACTI_Date, label = TRUE),
                           weekend = 
                             case_when(weekday == 'Fri' | weekday == 'Sat' ~ 1,
                                       .default = 0))
```

### Sleep Environment Variables

```{r}
# c_se_12_v2 -- sleep disruptions
# YES (1), NO (2)
table(models$c_se_12_v2, useNA = "always")

# c_se_8_v2 -- sleep quiet
# YES (1), NO (2)
table(models$c_se_8_v2, useNA = "always")

# # c_se_11_v2 -- sleep dark
# YES (1), NO (2)
table(models$c_se_11_v2, useNA = "always")
```


# Correlation Matrix

A correlation matrix was created for the variables of interest (dependent variables, covariates, and fixed effects). On the correlation matrix, darker colors (blue for positive; red for negative correlation) and bigger squares mean a stronger correlation. The area of the correlation matrix of most interest is the upper right most rectangle indicating correlations between the sleep variables (labeled "dependent variables") and the environment variables (labeled "fixed effects").

## Variables of interest

**DVs (sleep variables with models run for each sleep DV):**

Sleep Variables \[weekly level\]-

1.  Duration (C_ACTI_SleepTimeAvg)

2.  Timing

-   offset/waketime (C_ACTI_WTmean)

-   onset/falling asleep (C_ACTI_SleepOnsetTime_mean)

3.  Quality

-   efficiency (C_ACTI_EfficiencyAvg)

-   awakenings (C_ACTI_WasoAvg)

4.  Variability

-   Duration (C_ACTI_SleepTime_sd)

-   Timing

-   offset/waketime (C_ACTI_WTsd)

-   onset/falling asleep (C_ACTI_SleepOnsetTime_sd)

**Covariates:**

1.  Sex (c_demo_8_v2)

2.  Age (c_demo_2_v2)

3.  Grade in School (c_demo_6_v2)

4.  Caregiver Highest Education (parent 1: p_demo_26_v2; parent 2: p_demo_27_v2)

5.  School Year/Summer (C_DD_PM_DayType)

-   Note that this is only for Daily Diary

-   Needs to be calculated for Actigraphy (Use Date: C_ACTI_Date)

**Fixed Effects:**

Neighborhood Factors

1.  COI Total (geo_COI_3.0)

2.  COI Domains (3)

-   Education (geo_COI_ED_3.0)

-   Health & Environment (geo_COI_HE_3.0)

-   Social & Economic (geo_COI_SE_3.0)

Family Factors

1.  Family Cohesion Subscale \[higher = more cohesion\]

-   Parent report (P_COHESION)

-   Child report (C_COHESION; individual items are named frm)

2.  MESA

-   MESA Family Trouble Subscale \[score is event count; higher=more family trouble events\] (C_MESA_FT)

-   MESA Economic Stress Subscale \[score is event count; higher=more econ stress events\] (C_MESA_ES)

3.  Adol CHAOS Subscale \[higher=more chaos\] (C_CHAOS)

Sleep Environment Inventory

1.  SEI Sleep Aids Subscale \[interpret so that higher score reflects more sleep aids\] (C_SEI_SA)

2.  SEI Sleep Disturbances Subscale \[interpret so that higher score means less disturbance\] (C_SEI_SD)

3.  SEI Comfort Subscale \[interpret so that higher score means more comfortable environment\] (C_SEI_C)

```{r}
all %>%
  select(
    SleepTimeAvg = C1_ACTI_SL_SleepTimeAvg,
    WTmean = C1_ACTI_WTmean,
    SOT_mean = C1_ACTI_SleepOnsetTime_mean,
    EfficiencyAvg = C1_ACTI_SL_EfficiencyAvg,
    WasoAvg = C1_ACTI_SL_WasoAvg,
    SleepTimeSd = C1_ACTI_SL_SleepTimeSd,
    WakeTimeSd = C1_ACTI_SL_WakeTimeSd,
    SleepOnsetSd = C1_ACTI_SL_SleepTimeSd,
    age = c_demo_2_v2,
    sex = c_demo_8_v2,
    grade_in_school = c_demo_6_v2,
    cg_highest_ed1 = p_demo_26_v2,
    cg_highest_ed2 = p_demo_27_v2,
    school_summer = C_DD_PM_DayType,
    COItotal = geo_COI_3.0, 
    COI_ED = geo_COI_ED_3.0,
    COI_HE = geo_COI_HE_3.0,
    COI_SE = geo_COI_SE_3.0,
    P_COHESION, 
    C_COHESION,
    C_MESA_FT,
    C_MESA_ES,
    C_CHAOS,
    C_SEI_SA,
    C_SEI_SD,
    C_SEI_C
  ) %>% cor(use = "pairwise.complete.obs") %>% corrplot(method = "square", tl.cex = 0.5, addCoef.col = "black", number.cex = 0.3) %>% corrRect(name = c("SleepTimeAvg","age","COItotal","C_SEI_C"))
```

Notably, there is a moderate positive correlation between average sleep time and COI total and COI Social and Economic. There is a moderate negative correlation between average sleep time and parent report of family cohesion.

There is a moderate positive correlation between mean wake time and SEI Sleep Aids Subscale. Mean wake time does not have a significant negative correlation with any environmental variables.

Falling asleep time has a moderate positive correlation with SEI Sleep Aids Subscale, but no significant negative correlations with another variable.

Average efficiency has a moderate positive correlation with MESA Family Trouble Subscale and a moderate negative correlation with parent report of family cohesion.

Wake time standard deviation has a moderate positive correlation with MESA Economic Stress Subscale, but it does not have a significant negative correlation with any environmental variables.

Awakenings quality (WASO), sleep duration standard deviation, and sleep onset time standard deviation do not have any significant correlations with environmental variables.



\newpage

# Models

We are interested in 9 dependent variables: sleep duration, offset/waketime, onset/falling asleep time, efficiency, awakenings, duration variability, offset variation, and onset variation. There are 3 models for each dependent variable. The first model includes neighborhood factors (COI domains). The second model includes family factors (family cohesion, MESA variables, and CHAOS). The third model includes sleep environment characteristics (number of sleep disruptions and if the environment was quiet). Originally, the third model was to also include if the environment was dark, but only one individual had a light environment, so this variable is not usable.

Each model also includes covariates: sex, grade, and whether the study day was during the school year or summer. We also derived a new variable for whether the study day was a weekend (Friday or Saturday night). The levels in the grade in school variable were renamed to reflect the number of the grade. An individual also had grade level 7, which was not defined on the scale. Because the individual was 13, we put them into grade level 1, which is 8th grade.

BASIC MODEL: includes c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType

## Daily Variables

### Duration (C_ACTI_Duration)

```{r}
hist(all$C_ACTI_Duration)
summary(all$C_ACTI_Duration)

################################
#Model 1: Neighborhood Factors
################################
mod1_duration <- lmer(C_ACTI_Duration ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + weekend + geo_COI_ED_3.0 + geo_COI_HE_3.0 + geo_COI_SE_3.0 + (1|ParticipantID), data = models %>% filter(c_demo_6_v2 %in% c(8,9,10,11,12)))
summary(mod1_duration)
ci <- confint(mod1_duration)
print(ci)

plot(mod1_duration, type=c("p","smooth"), col.line=1)

plot(mod1_duration,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod1_duration)


################################
#Model 2: Family Factors
################################
mod2_duration <- lmer(C_ACTI_Duration ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS + (1|ParticipantID), data = models %>% filter(c_demo_6_v2 %in% c(8,9,10,11,12))
summary(mod2_duration)
ci <- confint(mod2_duration)
print(ci)

plot(mod2_duration, type=c("p","smooth"), col.line=1)

plot(mod2_duration,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod2_duration)


################################
#Model 3: Sleep Environment Characteristics
################################
mod3_duration <- lmer(C_ACTI_Duration ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + c_se_12_v2 + c_se_8_v2 + c_se_11_v2 + (1|ParticipantID), data = models %>% filter(c_demo_6_v2 %in% c(8,9,10,11,12))
summary(mod3_duration)
ci <- confint(mod3_duration)
print(ci)

plot(mod3_duration, type=c("p","smooth"), col.line=1)

plot(mod3_duration,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod3_duration)
```

\newpage

### Offset/Wake Time (C_ACTI_WT_DEC)

```{r}
hist(all$C_ACTI_WT_DEC)
summary(all$C_ACTI_WT_DEC)

################################
#Model 1: Neighborhood Factors
################################
mod1_offset <- lmer(C_ACTI_WT_DEC ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + geo_COI_ED_3.0 + geo_COI_HE_3.0 + geo_COI_SE_3.0 + (1|ParticipantID), data = models)
summary(mod1_offset)
ci <- confint(mod1_offset)
print(ci)

plot(mod1_offset, type=c("p","smooth"), col.line=1)

plot(mod1_offset,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod1_offset)


################################
#Model 2: Family Factors
################################
mod2_offset <- lmer(C_ACTI_WT_DEC ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS + (1|ParticipantID), data = models)
summary(mod2_offset)
ci <- confint(mod2_offset)
print(ci)

plot(mod2_offset, type=c("p","smooth"), col.line=1)

plot(mod2_offset,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod2_offset)


################################
#Model 3: Sleep Environment Characteristics
################################
mod3_offset <- lmer(C_ACTI_WT_DEC ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + c_se_12_v2 + c_se_8_v2 + (1|ParticipantID), data = models)
summary(mod3_offset)
ci <- confint(mod3_offset)
print(ci)

plot(mod3_offset, type=c("p","smooth"), col.line=1)

plot(mod3_offset,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod3_offset)
```

\newpage

### Onset/Falling Asleep (C_ACTI_SOL)

```{r}
hist(all$C_ACTI_SOL)
summary(all$C_ACTI_SOL)

################################
#Model 1: Neighborhood Factors
################################
mod1_onset1 <- lmer(C_ACTI_SOL ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + geo_COI_ED_3.0 + geo_COI_HE_3.0 + geo_COI_SE_3.0 + (1|ParticipantID), data = models)
summary(mod1_onset1)
ci <- confint(mod1_onset1)
print(ci)

plot(mod1_onset1, type=c("p","smooth"), col.line=1)

plot(mod1_onset1,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod1_onset1)


################################
#Model 2: Family Factors
################################
mod2_onset1 <- lmer(C_ACTI_SOL ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS + (1|ParticipantID), data = models)
summary(mod2_onset1)
ci <- confint(mod2_onset1)
print(ci)

plot(mod2_onset1, type=c("p","smooth"), col.line=1)

plot(mod2_onset1,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod2_onset1)


################################
#Model 3: Sleep Environment Characteristics
################################
mod3_onset1 <- lmer(C_ACTI_SOL ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + c_se_12_v2 + c_se_8_v2 + (1|ParticipantID), data = models)
summary(mod3_onset1)
ci <- confint(mod3_onset1)
print(ci)

plot(mod3_onset1, type=c("p","smooth"), col.line=1)

plot(mod3_onset1,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod3_onset1)
```

\newpage

### Onset/Falling Asleep 2 (C_ACTI_SleepOnsetTime_TRM)

```{r}
hist(all$C_ACTI_SleepOnsetTime_TRM)
summary(all$C_ACTI_SleepOnsetTime_TRM)

################################
#Model 1: Neighborhood Factors
################################
mod1_onset2 <- lmer(C_ACTI_SOL ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + geo_COI_ED_3.0 + geo_COI_HE_3.0 + geo_COI_SE_3.0 + (1|ParticipantID), data = models)
summary(mod1_onset2)
ci <- confint(mod1_onset2)
print(ci)

plot(mod1_onset2, type=c("p","smooth"), col.line=1)

plot(mod1_onset2,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod1_onset2)


################################
#Model 2: Family Factors
################################
mod2_onset2 <- lmer(C_ACTI_SOL ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS + (1|ParticipantID), data = models)
summary(mod2_onset2)
ci <- confint(mod2_onset2)
print(ci)

plot(mod2_onset2, type=c("p","smooth"), col.line=1)

plot(mod2_onset2,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod2_onset2)


################################
#Model 3: Sleep Environment Characteristics
################################
mod3_onset2 <- lmer(C_ACTI_SOL ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + c_se_12_v2 + c_se_8_v2 + (1|ParticipantID), data = models)
summary(mod3_onset2)
ci <- confint(mod3_onset2)
print(ci)

plot(mod3_onset2, type=c("p","smooth"), col.line=1)

plot(mod3_onset2,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod3_onset2)
```

\newpage

### Efficiency (C_ACTI_Efficiency)

```{r}
hist(all$C_ACTI_Efficiency)
summary(all$C_ACTI_Efficiency)

################################
#Model 1: Neighborhood Factors
################################
mod1_efficiency <- lmer(C_ACTI_Efficiency ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + geo_COI_ED_3.0 + geo_COI_HE_3.0 + geo_COI_SE_3.0 + (1|ParticipantID), data = models)
summary(mod1_efficiency)
ci <- confint(mod1_efficiency)
print(ci)

plot(mod1_efficiency, type=c("p","smooth"), col.line=1)

plot(mod1_efficiency,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod1_efficiency)


################################
#Model 2: Family Factors
################################
mod2_efficiency <- lmer(C_ACTI_Efficiency ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS + (1|ParticipantID), data = models)
summary(mod2_efficiency)
ci <- confint(mod2_efficiency)
print(ci)

plot(mod2_efficiency, type=c("p","smooth"), col.line=1)

plot(mod2_efficiency,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod2_efficiency)


################################
#Model 3: Sleep Environment Characteristics
################################
mod3_efficiency <- lmer(C_ACTI_Efficiency ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + c_se_12_v2 + c_se_8_v2 + (1|ParticipantID), data = models)
summary(mod3_efficiency)
ci <- confint(mod3_efficiency)
print(ci)

plot(mod3_efficiency, type=c("p","smooth"), col.line=1)

plot(mod3_efficiency,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod3_efficiency)
```

\newpage

### Awakenings (C_ACTI_Waso)

```{r}
hist(all$C_ACTI_Waso)
summary(all$C_ACTI_Waso)

################################
#Model 1: Neighborhood Factors
################################
mod1_waso <- lmer(C_ACTI_Waso ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + geo_COI_ED_3.0 + geo_COI_HE_3.0 + geo_COI_SE_3.0 + (1|ParticipantID), data = models)
summary(mod1_waso)
ci <- confint(mod1_waso)
print(ci)

plot(mod1_waso, type=c("p","smooth"), col.line=1)

plot(mod1_waso,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod1_waso)


################################
#Model 2: Family Factors
################################
mod2_waso <- lmer(C_ACTI_Waso ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS + (1|ParticipantID), data = models)
summary(mod2_waso)
ci <- confint(mod2_waso)
print(ci)

plot(mod2_waso, type=c("p","smooth"), col.line=1)

plot(mod2_waso,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod2_waso)


################################
#Model 3: Sleep Environment Characteristics
################################
mod3_waso <- lmer(C_ACTI_Waso ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + c_se_12_v2 + c_se_8_v2 + (1|ParticipantID), data = models)
summary(mod3_waso)
ci <- confint(mod3_waso)
print(ci)

plot(mod3_waso, type=c("p","smooth"), col.line=1)

plot(mod3_waso,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(mod3_waso)
```

\newpage

## Weekly Variables

```{r}
weekly <- models %>% filter(StudyDay == 1)
```


### Duration Variability (C_ACTI_SleepTime_sd)

```{r}
hist(all$C_ACTI_SleepTime_sd)
summary(all$C_ACTI_SleepTime_sd)

################################
#Model 1: Neighborhood Factors
################################
mod1_dur_var <- lm(C_ACTI_SleepTime_sd ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + geo_COI_ED_3.0 + geo_COI_HE_3.0 + geo_COI_SE_3.0, data = weekly)
summary(mod1_dur_var)
ci <- confint(mod1_dur_var)
print(ci)

plot(mod1_dur_var, 1)
plot(mod1_dur_var, 2)


################################
#Model 2: Family Factors
################################
mod2_dur_var <- lm(C_ACTI_SleepTime_sd ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS, data = weekly)
summary(mod2_dur_var)
ci <- confint(mod2_dur_var)
print(ci)

plot(mod2_dur_var, 1)
plot(mod2_dur_var, 2)


################################
#Model 3: Sleep Environment Characteristics
################################
mod3_dur_var <- lm(C_ACTI_SleepTime_sd ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + c_se_12_v2 + c_se_8_v2, data = weekly)
summary(mod3_dur_var)
ci <- confint(mod3_dur_var)
print(ci)

plot(mod3_dur_var, 1)
plot(mod3_dur_var, 2)
```

\newpage

### Offset Variability (C_ACTI_WakeTime_sd)

```{r}
hist(all$C_ACTI_WakeTime_sd)
summary(all$C_ACTI_WakeTime_sd)

################################
#Model 1: Neighborhood Factors
################################
mod1_off_var <- lm(C_ACTI_WakeTime_sd ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + geo_COI_ED_3.0 + geo_COI_HE_3.0 + geo_COI_SE_3.0, data = weekly)
summary(mod1_off_var)
ci <- confint(mod1_off_var)
print(ci)

plot(mod1_off_var, 1)
plot(mod1_off_var, 2)


################################
#Model 2: Family Factors
################################
mod2_off_var <- lm(C_ACTI_WakeTime_sd ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS, data = weekly)
summary(mod2_off_var)
ci <- confint(mod2_off_var)
print(ci)

plot(mod2_off_var, 1)
plot(mod2_off_var, 2)


################################
#Model 3: Sleep Environment Characteristics
################################
mod3_off_var <- lm(C_ACTI_WakeTime_sd ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + c_se_12_v2 + c_se_8_v2, data = weekly)
summary(mod3_off_var)
ci <- confint(mod3_off_var)
print(ci)

plot(mod3_off_var, 1)
plot(mod3_off_var, 2)
```

\newpage

### Onset Variability (C_ACTI_SleepTime_sd)

```{r}
hist(all$C_ACTI_SleepTime_sd)
summary(all$C_ACTI_SleepTime_sd)

################################
#Model 1: Neighborhood Factors
################################
mod1_on_var <- lm(C_ACTI_SleepTime_sd ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + geo_COI_ED_3.0 + geo_COI_HE_3.0 + geo_COI_SE_3.0, data = weekly)
summary(mod1_on_var)
ci <- confint(mod1_on_var)
print(ci)

plot(mod1_on_var, 1)
plot(mod1_on_var, 2)


################################
#Model 2: Family Factors
################################
mod2_on_var <- lm(C_ACTI_SleepTime_sd ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS, data = weekly)
summary(mod2_on_var)
ci <- confint(mod2_on_var)
print(ci)

plot(mod2_on_var, 1)
plot(mod2_on_var, 2)


################################
#Model 3: Sleep Environment Characteristics
################################
mod3_on_var <- lm(C_ACTI_SleepTime_sd ~ c_demo_8_v2 + c_demo_6_v2 + C_DD_PM_DayType + c_se_12_v2 + c_se_8_v2, data = weekly)
summary(mod3_on_var)
ci <- confint(mod3_on_var)
print(ci)

plot(mod3_on_var, 1)
plot(mod3_on_var, 2)
```
