---
title: "Updated Neighborhood Analysis"
format: html
editor: visual
---

# PUSH Sleep and Neighborhood Effects

```{r message = FALSE, warning=FALSE}
library(corrplot)
library(tidyverse)


# diary and actigraphy data
push_long <- read_csv("PUSH_long_acti_diary_3.23.2026.csv") %>% 
  rename(ParticipantID = 'Global Participant ID')

# survey data
push_wide <- read_csv("PUSH_actigraph_survey_geo_wide_8.7.25.csv")
```

### Merge Datasets

```{r}
# left join
all <- left_join(push_long, push_wide, by = "ParticipantID")

# remove people who do not have actigraphy data?
all <- all %>% filter(Data_Source != 'Diary')

dim(all)
all %>% group_by(ParticipantID) %>% summarize(days = n()) 

all %>% group_by(ParticipantID) %>% summarize(days = n()) %>% ungroup() %>% group_by(days) %>% summarize(n = n())
```

## EDA

We began by observing the distribution of the independent variables of interest (dependent variable distributions are observed with their models below).

```{r}
vars <- all %>% select(ParticipantID, merge_study_day, C_ACTI_Date,
                         # dependent vars
                         C_ACTI_SleepTime, 
                         C_ACTI_WT_DEC, 
                         C_ACTI_SOL, 
                         C_ACTI_SleepOnsetTime_TRM, 
                         C_ACTI_Efficiency, 
                         C_ACTI_Waso, 
                         C_ACTI_SleepTime_sd, 
                         C_ACTI_WT_DEC_sd,
                         C_ACTI_WakeTime_sd,
                         C_ACTI_SleepOnsetTime_TRM_sd, 
                         # covariates
                         c_demo_8_v2, 
                         c_demo_6_v2, 
                         `Day Type`,
                         #fixed effects
                         geo_COI_3.0,
                         geo_COI_ED_3.0,
                         geo_COI_HE_3.0,
                         geo_COI_SE_3.0,
                         P_COHESION,
                         C_MESA_FT,
                         C_MESA_ES,
                         C_CHAOS,
                         c_se_12_v2,
                         c_se_8_v2,
                         c_se_11_v2) %>% 
  rename(Day_Type = `Day Type`) %>% 
  mutate(c_demo_8_v2 = as.factor(c_demo_8_v2),
         Day_Type = as.factor(Day_Type),
         c_se_12_v2 = as.factor(c_se_12_v2),
         c_se_8_v2 = as.factor(c_se_8_v2),
         c_se_11_v2 = as.factor(c_se_11_v2))
```

### Fix Covariates

Fix school year so people labeled '7' are labeled as '8'.

Add weekend variable

```{r}
# c_demo_8_v2 -- Biological Sex
# MALE (1), FEMALE (2), DON’T KNOW (3), PREFER NOT TO ANSWER (4)
table(vars$c_demo_8_v2, useNA = "always")

# c_demo_6_v2 -- Grade in School
# 8th (1), 9th (2), 10th (3), 11th (4), 12th (5)
table(vars$c_demo_6_v2, useNA = "always")
all %>% filter(c_demo_6_v2 == 7) %>% select(c_demo_6_v2, c_demo_2_v2)

model <- vars %>% mutate(c_demo_6_v2 = case_when(
  c_demo_6_v2 == 1 ~ 8,
  c_demo_6_v2 == 2 ~ 9,
  c_demo_6_v2 == 3 ~ 10,
  c_demo_6_v2 == 4 ~ 11,
  c_demo_6_v2 == 5 ~ 12,
  c_demo_6_v2 == 7 ~ 8))
table(model$c_demo_6_v2, useNA = "always")

# C_DD_PM_DayType -- School or Summer
# Summer (0), Academic School Year (1)
table(model$Day_Type)

# add weekend variable
  # weekend = Friday or Saturday night
models <- model %>% mutate(weekday = wday(model$C_ACTI_Date, label = TRUE),
                           weekend = 
                             case_when(weekday == 'Fri' | weekday == 'Sat' ~ 1,
                                       .default = 0))
```

### Fix Sleep Variables

The three sleep environment variables are sleep disruptions, sleep quiet, and sleep dark. Notably, sleep dark is true for all individuals except for one. Because only one person does not have a dark sleep environment, this variable cannot be used in the models.

```{r}
# c_se_12_v2 -- sleep disruptions
# YES (1), NO (2)
table(models$c_se_12_v2, useNA = "always")

# c_se_8_v2 -- sleep quiet
# YES (1), NO (2)
table(models$c_se_8_v2, useNA = "always")

# # c_se_11_v2 -- sleep dark
# YES (1), NO (2)
table(models$c_se_11_v2, useNA = "always")
```

\newpage

# Models

We are interested in 7 dependent variables: sleep duration, offset/waketime, onset/falling asleep time, efficiency, duration variability, offset variation, and onset variation. There are 3 models for each dependent variable. The first model includes neighborhood factors (COI domains), the second model includes family factors (family cohesion, MESA variables, and CHAOS), and the third model includes sleep environment characteristics (number of sleep disruptions and if the environment was quiet). Originally, the third model was to also include if the environment was dark, but only one individual had a light environment, so this variable is not usable in the model.

Each model also includes covariates: sex, grade, whether the study day was during the school year or summer, and whether the study day was a weekend (Friday or Saturday night). The levels in the grade in school variable were renamed to reflect the number of the grade. An individual also had grade level 7, which was not defined on the scale. Because the individual was 13, we put them into grade level 1, which is 8th grade.

**Neighborhood Model**: response \~ geo_COI_3.0 + geo_COI_ED_3.0 + geo_COI_HE_3.0 + geo_COI_SE_3.0 + c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend + (1\|ParticipantID)

**Family Model:** response \~ P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS + c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend + (1\|ParticipantID)

**Sleep Environment Model**: response \~ c_se_12_v2 + c_se_8_v2 + c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend + (1\|ParticipantID)

## Daily

### Sleep Duration (C_ACTI_SleepTime)

```{r}
library(lme4)
library(lmerTest)
# Neighborhood Factors: Do I include COI_3.0 or just the subdomains?
nbhd_dur <- lmer(C_ACTI_SleepTime ~ geo_COI_3.0 + geo_COI_ED_3.0 + geo_COI_HE_3.0 +
                   geo_COI_SE_3.0 + c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend +
                   (1|ParticipantID), data = models)
summary(nbhd_dur)
confint(nbhd_dur)

# Family Factors
fmly_dur <- lmer(C_ACTI_SleepTime ~ P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS +
                   c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend + (1|ParticipantID),
                 data = models)
summary(fmly_dur)
confint(fmly_dur)

# Sleep Environment Factors
senv_dur <- lmer(C_ACTI_SleepTime ~ c_se_12_v2 + c_se_8_v2 + c_demo_8_v2 +
                   c_demo_6_v2 + Day_Type + weekend + (1|ParticipantID), data = models)

summary(senv_dur)
confint(senv_dur)
```

### Offset/Waketime (C_ACTI_WT_DEC)

```{r}
# Neighborhood
nbhd_off <- lmer(C_ACTI_WT_DEC ~ geo_COI_3.0 + geo_COI_ED_3.0 + geo_COI_HE_3.0 +
                   geo_COI_SE_3.0 + c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend +
                   (1|ParticipantID), data = models)
summary(nbhd_off)
confint(nbhd_off)

# Family
fmly_off <- lmer(C_ACTI_WT_DEC ~ P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS +
                   c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend + (1|ParticipantID),
                 data = models)
summary(fmly_off)
confint(fmly_off)

# Sleep Environment
senv_off <- lmer(C_ACTI_WT_DEC ~ c_se_12_v2 + c_se_8_v2 + c_demo_8_v2 + c_demo_6_v2 + 
                   Day_Type + weekend + (1|ParticipantID), data = models)
summary(senv_off)
confint(senv_off)
```

### Onset/Falling Asleep Time (C_ACTI_SOL)

```{r}
# Neighborhood
nbhd_on <- lmer(C_ACTI_SOL ~ geo_COI_3.0 + geo_COI_ED_3.0 + geo_COI_HE_3.0 +
                   geo_COI_SE_3.0 + c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend +
                   (1|ParticipantID), data = models)
summary(nbhd_on)
confint(nbhd_on)

# Family
fmly_on <- lmer(C_ACTI_SOL ~ P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS +
                   c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend + (1|ParticipantID),
                 data = models)
summary(fmly_on)
confint(fmly_on)

# Sleep Environment
senv_on <- lmer(C_ACTI_SOL ~ c_se_12_v2 + c_se_8_v2 + c_demo_8_v2 + c_demo_6_v2 + 
                   Day_Type + weekend + (1|ParticipantID), data = models)
summary(senv_on)
confint(senv_on)
```

### Efficiency (C_ACTI_Efficiency)

```{r}
# Neighborhood
nbhd_eff <- lmer(C_ACTI_Efficiency ~ geo_COI_3.0 + geo_COI_ED_3.0 + geo_COI_HE_3.0 +
                   geo_COI_SE_3.0 + c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend +
                   (1|ParticipantID), data = models)
summary(nbhd_eff)
confint(nbhd_eff)

# Family
fmly_eff <- lmer(C_ACTI_Efficiency ~ P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS +
                   c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend + (1|ParticipantID),
                 data = models)
summary(fmly_eff)
confint(fmly_eff)

# Sleep Environment
senv_eff <- lmer(C_ACTI_Efficiency ~ c_se_12_v2 + c_se_8_v2 + c_demo_8_v2 + 
                  c_demo_6_v2 + Day_Type + weekend + (1|ParticipantID), data = models)
summary(senv_eff)
confint(senv_eff)
```

## Weekly/Weekend Variables

### Duration Variability (C_ACTI_SleepTime_sd)

```{r}
weekly <- models %>% filter(merge_study_day == 1)

# Neighborhood
nbhd_dursd <- lm(C_ACTI_SleepTime_sd ~ geo_COI_3.0 + geo_COI_ED_3.0 + 
                     geo_COI_HE_3.0 + geo_COI_SE_3.0 + c_demo_8_v2 + c_demo_6_v2 +
                     Day_Type + weekend, data = weekly)
summary(nbhd_dursd)
confint(nbhd_dursd)

# Family
fmly_dursd <- lm(C_ACTI_SleepTime_sd ~ P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS +
                   c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend, data = weekly)
summary(fmly_dursd)
confint(fmly_dursd)

# Sleep Environment
senv_dursd <- lm(C_ACTI_SleepTime_sd ~ c_se_12_v2 + c_se_8_v2 + c_demo_8_v2 +
                   c_demo_6_v2 + Day_Type + weekend, data = weekly)
summary(senv_dursd)
confint(senv_dursd)
```

### Offset Variation (C_ACTI_WT_DEC_sd)

```{r}
# Neighborhood
nbhd_offsd <- lm(C_ACTI_WT_DEC_sd ~ geo_COI_3.0 + geo_COI_ED_3.0 + geo_COI_HE_3.0 +
                   geo_COI_SE_3.0 + c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend,
                 data = weekly)
summary(nbhd_offsd)
confint(nbhd_offsd)

# Family
fmly_offsd <- lm(C_ACTI_WT_DEC_sd ~ P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS +
                   c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend, data = weekly)
summary(fmly_offsd)
confint(fmly_offsd)

# Sleep Environment
senv_offsd <- lm(C_ACTI_WT_DEC_sd ~ c_se_12_v2 + c_se_8_v2 + c_demo_8_v2 +
                   c_demo_6_v2 + Day_Type + weekend, data = weekly)
summary(senv_offsd)
confint(senv_offsd)
```

### Onset Variation (C_ACTI_SleepOnsetTime_TRM_sd)

```{r}
# Neighborhood
nbhd_onsd <- lm(C_ACTI_SleepOnsetTime_TRM_sd ~ geo_COI_3.0 + geo_COI_ED_3.0 +
                  geo_COI_HE_3.0 + geo_COI_SE_3.0 + c_demo_8_v2 + c_demo_6_v2 +
                  Day_Type + weekend, data = weekly)
summary(nbhd_onsd)
confint(nbhd_onsd)

# Family 
fmly_onsd <- lm(C_ACTI_SleepOnsetTime_TRM_sd ~ P_COHESION + C_MESA_FT + C_MESA_ES +
                  C_CHAOS + c_demo_8_v2 + c_demo_6_v2 + Day_Type + weekend, 
                data = weekly)
summary(fmly_onsd)
confint(fmly_onsd)

# Sleep Environment
senv_onsd <- lm(C_ACTI_SleepOnsetTime_TRM_sd ~ c_se_12_v2 + c_se_8_v2 + c_demo_8_v2 +
                   c_demo_6_v2 + Day_Type + weekend, data = weekly)
summary(senv_onsd)
confint(senv_onsd)
```

# Oliver Notes (3/30)

## Questions

For the Neighborhood models, do I include COI_3.0 (seems like the overall variable) as the only neighborhood exp. variable or the domains?

I'm generally confused re: the differences between the "Daily", "Weekly", and "Weekend" models. Why is the weekly dataset only the first day of the study? Am I missing something here?

## Comments

### Coef Significance/Confidence Intervals

Without getting specific, a lot of these models look capital B bad. The only ones that seemed to have any significance were the family factor models. A lot of this stuff was consistent throughout each model, though, so there is still a story to be told.

# Model Analysis Summary
