---
title: "Updated PUSH Sleep and Neighborhood Effects"
author: "Josie Peterburs and Oliver Schramm"
date: today
format: html
editor: visual
---

# Data Cleaning

```{r message = FALSE, warning=FALSE}
library(corrplot)
library(tidyverse)
library(lme4)
library(lmerTest)

# diary and actigraphy data
push_long <- read_csv("PUSH_long_acti_diary_3.23.2026.csv") %>% 
  rename(ParticipantID = 'Global Participant ID')

# survey data
push_wide <- read_csv("PUSH_actigraph_survey_geo_wide_8.7.25.csv")
```

### Merge Datasets

```{r}
# left join
all <- left_join(push_long, push_wide, by = "ParticipantID")

# remove people who do not have actigraphy data?
all <- all %>% filter(Data_Source != 'Diary')

dim(all)
all %>% group_by(ParticipantID) %>% summarize(days = n()) 

all %>% group_by(ParticipantID) %>% summarize(days = n()) %>% ungroup() %>% group_by(days) %>% summarize(n = n())
```

## EDA

We began by observing the distribution of the independent variables of interest (dependent variable distributions are observed with their models below).

```{r}
vars <- all %>% select(ParticipantID, merge_study_day, C_ACTI_Date,
                         # dependent vars
                         C_ACTI_SleepTime, 
                         C_ACTI_WT_DEC, 
                         C_ACTI_SOL, 
                         C_ACTI_SleepOnsetTime_TRM, 
                         C_ACTI_Efficiency, 
                         C_ACTI_Waso, 
                         C_ACTI_SleepTime_sd, 
                         C_ACTI_WT_DEC_sd,
                         C_ACTI_WakeTime_sd,
                         C_ACTI_SleepOnsetTime_TRM_sd, 
                         # covariates
                         c_demo_8_v2, 
                         c_demo_6_v2, 
                         `Day Type`,
                         #fixed effects
                         geo_COI_3.0,
                         geo_COI_ED_3.0,
                         geo_COI_HE_3.0,
                         geo_COI_SE_3.0,
                         P_COHESION,
                         C_MESA_FT,
                         C_MESA_ES,
                         C_CHAOS,
                         c_se_12_v2,
                         c_se_8_v2,
                         c_se_11_v2) %>% 
  rename(Day_Type = `Day Type`) %>% 
  mutate(c_demo_8_v2 = as.factor(c_demo_8_v2),
         Day_Type = as.factor(Day_Type),
         c_se_12_v2 = as.factor(c_se_12_v2),
         c_se_8_v2 = as.factor(c_se_8_v2),
         c_se_11_v2 = as.factor(c_se_11_v2))
```

### Fix Covariates

Fixed school year so people labeled '7' are labeled as '8'.

Added weekend variable.

```{r}
# c_demo_8_v2 -- Biological Sex
# MALE (1), FEMALE (2), DON’T KNOW (3), PREFER NOT TO ANSWER (4)
table(vars$c_demo_8_v2, useNA = "always")

# c_demo_6_v2 -- Grade in School
# 8th (1), 9th (2), 10th (3), 11th (4), 12th (5)
table(vars$c_demo_6_v2, useNA = "always")
all %>% filter(c_demo_6_v2 == 7) %>% select(c_demo_6_v2, c_demo_2_v2)

model <- vars %>% mutate(c_demo_6_v2 = case_when(
  c_demo_6_v2 == 1 ~ 8,
  c_demo_6_v2 == 2 ~ 9,
  c_demo_6_v2 == 3 ~ 10,
  c_demo_6_v2 == 4 ~ 11,
  c_demo_6_v2 == 5 ~ 12,
  c_demo_6_v2 == 7 ~ 8))
table(model$c_demo_6_v2, useNA = "always")

# C_DD_PM_DayType -- School or Summer
# Summer (0), Academic School Year (1)
table(model$Day_Type)

# add weekend variable
  # weekend = Friday or Saturday night
models <- model %>% mutate(weekday = wday(model$C_ACTI_Date, label = TRUE),
                           weekend = 
                             case_when(weekday == 'Fri' | weekday == 'Sat' ~ 1,
                                       .default = 0))
```

### Fix Sleep Variables

The three sleep environment variables are sleep disruptions, sleep quiet, and sleep dark. Notably, sleep dark is true for all individuals except for one. Because only one person does not have a dark sleep environment, this variable cannot be used in the models.

```{r}
# c_se_12_v2 -- sleep disruptions
# YES (1), NO (2)
table(models$c_se_12_v2, useNA = "always")

# c_se_8_v2 -- sleep quiet
# YES (1), NO (2)
table(models$c_se_8_v2, useNA = "always")

# # c_se_11_v2 -- sleep dark
# YES (1), NO (2)
table(models$c_se_11_v2, useNA = "always")
```

\newpage

# Models

We are interested in 7 dependent variables: sleep duration, offset/waketime, onset/falling asleep time, efficiency, duration variability, offset variation, and onset variation. 

There are 2 models for each dependent variable. The first model includes neighborhood factors (COI domains) and the second model includes family factors (family cohesion, MESA variables, and CHAOS).

Each model also includes covariates: sex, grade, and whether the study day was a weekend (Friday or Saturday night). The levels in the grade in school variable were renamed to reflect the number of the grade. An individual also had grade level 7, which was not defined on the scale. Because the individual was 13, we put them into grade level 1, which is 8th grade.

**Neighborhood Model**: response \~ geo_COI_3.0 + c_demo_8_v2 + c_demo_6_v2 + weekend + (1\|ParticipantID)

**Family Model:** response \~ P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS + c_demo_8_v2 + c_demo_6_v2 + weekend + (1\|ParticipantID)

## Daily Variables

### Sleep Duration (C_ACTI_SleepTime)

```{r}
# Neighborhood Factors: Do I include COI_3.0 or just the subdomains?
nbhd_dur <- lmer(C_ACTI_SleepTime ~ geo_COI_3.0 + c_demo_8_v2 + c_demo_6_v2 + 
                   weekend + (1|ParticipantID), data = models)
summary(nbhd_dur)
confint(nbhd_dur)

plot(nbhd_dur, type=c("p","smooth"), col.line=1)

plot(nbhd_dur,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(nbhd_dur)

# Family Factors
fmly_dur <- lmer(C_ACTI_SleepTime ~ P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS + 
                   c_demo_8_v2 + c_demo_6_v2 + weekend + (1|ParticipantID),
                 data = models)
summary(fmly_dur)
confint(fmly_dur)

plot(fmly_dur, type=c("p","smooth"), col.line=1)

plot(fmly_dur,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(fmly_dur)
```

### Offset/Waketime (C_ACTI_WT_DEC)

```{r}
# Neighborhood
nbhd_off <- lmer(C_ACTI_WT_DEC ~ geo_COI_3.0 + c_demo_8_v2 + c_demo_6_v2 + 
                   weekend + (1|ParticipantID), data = models)
summary(nbhd_off)
confint(nbhd_off)

plot(nbhd_off, type=c("p","smooth"), col.line=1)

plot(nbhd_off,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(nbhd_off)

# Family
fmly_off <- lmer(C_ACTI_WT_DEC ~ P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS +
                   c_demo_8_v2 + c_demo_6_v2 + weekend + (1|ParticipantID),
                 data = models)
summary(fmly_off)
confint(fmly_off)

plot(fmly_off, type=c("p","smooth"), col.line=1)

plot(fmly_off,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(fmly_off)
```

### Onset/Falling Asleep Time (C_ACTI_SOL)

```{r}
# Neighborhood
nbhd_on <- lmer(log(C_ACTI_SOL+1) ~ geo_COI_3.0 + c_demo_8_v2 + c_demo_6_v2 + 
                   weekend + (1|ParticipantID), data = models)
summary(nbhd_on)
confint(nbhd_on)

plot(nbhd_on, type=c("p","smooth"), col.line=1)

plot(nbhd_on,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(nbhd_on)

# Family
fmly_on <- lmer(log(C_ACTI_SOL+1) ~ P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS +
                  c_demo_8_v2 + c_demo_6_v2 + weekend + (1|ParticipantID),
                 data = models)
summary(fmly_on)
confint(fmly_on)

plot(fmly_on, type=c("p","smooth"), col.line=1)

plot(fmly_on,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(fmly_on)

```

### Efficiency (C_ACTI_Efficiency)

```{r}
# Neighborhood
nbhd_eff <- lmer(C_ACTI_Efficiency ~ geo_COI_3.0 + c_demo_8_v2 + c_demo_6_v2 + 
                   weekend + (1|ParticipantID), data = models)
summary(nbhd_eff)
confint(nbhd_eff)

plot(nbhd_eff, type=c("p","smooth"), col.line=1)

plot(nbhd_eff,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(nbhd_eff)

# Family
fmly_eff <- lmer(C_ACTI_Efficiency ~ P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS +
                   c_demo_8_v2 + c_demo_6_v2 + weekend + (1|ParticipantID),
                 data = models)
summary(fmly_eff)
confint(fmly_eff)

plot(fmly_eff, type=c("p","smooth"), col.line=1)

plot(fmly_eff,
     sqrt(abs(resid(.)))~fitted(.),
     type=c("p","smooth"), col.line=1)

lattice::qqmath(fmly_eff)
```

## Weekly Variables

### Duration Variability (C_ACTI_SleepTime_sd)

```{r}
weekly <- models %>% filter(merge_study_day == 1)

# Neighborhood
nbhd_dursd <- lm(C_ACTI_SleepTime_sd ~ geo_COI_3.0 + c_demo_8_v2 + c_demo_6_v2 + 
                   weekend, data = weekly)
summary(nbhd_dursd)
confint(nbhd_dursd)

plot(nbhd_dursd, 1)
plot(nbhd_dursd, 2)

# Family
fmly_dursd <- lm(C_ACTI_SleepTime_sd ~ c_demo_8_v2 + c_demo_6_v2 + weekend +
                   P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS, data = weekly)
summary(fmly_dursd)
confint(fmly_dursd)

plot(fmly_dursd, 1)
plot(fmly_dursd, 2)
```

### Offset Variation (C_ACTI_WT_DEC_sd)

```{r}
# Neighborhood
nbhd_offsd <- lm(C_ACTI_WT_DEC_sd ~ geo_COI_3.0 + c_demo_8_v2 + c_demo_6_v2 + 
                   weekend, data = weekly)

summary(nbhd_offsd)
confint(nbhd_offsd)

plot(nbhd_offsd, 1)
plot(nbhd_offsd, 2)

# Family
fmly_offsd <- lm(C_ACTI_WT_DEC_sd ~ c_demo_8_v2 + c_demo_6_v2 + weekend +
                   P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS, data = weekly)
summary(fmly_offsd)
confint(fmly_offsd)

plot(fmly_offsd, 1)
plot(fmly_offsd, 2)
```

### Onset Variation (C_ACTI_SleepOnsetTime_TRM_sd)

```{r}
# Neighborhood
nbhd_onsd <- lm(C_ACTI_SleepOnsetTime_TRM_sd ~ geo_COI_3.0 + c_demo_8_v2 + 
                  c_demo_6_v2 + weekend, data = weekly)
summary(nbhd_onsd)
confint(nbhd_onsd)

plot(nbhd_onsd, 1)
plot(nbhd_onsd, 2)

# Family 
fmly_onsd <- lm(C_ACTI_SleepOnsetTime_TRM_sd ~ c_demo_8_v2 + c_demo_6_v2 + weekend +
                   P_COHESION + C_MESA_FT + C_MESA_ES + C_CHAOS, 
                data = weekly)
summary(fmly_onsd)
confint(fmly_onsd)

plot(fmly_onsd, 1)
plot(fmly_onsd, 2)
```

## Comments

### Coef Significance/Confidence Intervals

Without getting specific, a lot of these models look capital B bad. The only ones that seemed to have any significance were the family factor models. A lot of this stuff was consistent throughout each model, though, so there is still a story to be told.

# Model Analysis Summary
