---
title: "Period Pain and Sleep"
authors: 'Josie Peterburs, Oliver Schramm, Gregory J. Matthews'
format: html
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# Period Pain and Sleep Report

For this project, we want to study how being on your period affects sleep, specifically how period pain and flow affect sleep. We are interested in 6 sleep variables: duration, offset, onset, efficiency, awakenings, and the self-reported quality of sleep.

We have longitudinal data for two different time points for a number of individuals. The first time point is around menarche, and the second time point is about a year later. At each time point, there are about 8 days of data for each individual.

To get the final dataset, we combined 3 datasets:

- Empathy - personal and environmental variables

- Actigraphy 1 and 2 - sleep variables

- Daily Diary 1 and 2 - period variables (whether they are on their period)


```{r, include=FALSE}
library(tidyverse)
library(here)
library(lme4)

Empathy <- read_csv(here("Period_Pain/Data", "Empathy_Data_Updated.csv"))

actigraphy_t1 <- readxl::read_xlsx(here("Period_Pain/Data", "Esleep_T1_Sleep Data_DailyActi_4.22.25.xlsx"))

actigraphy_t2 <- readxl::read_xlsx(here("Period_Pain/Data", "Esleep_T2_Sleep Data_DailyActi_4.22.25.xlsx"))

diary_t1 <- readxl::read_xlsx(here("Period_Pain/Data", "E-Sleep_DailyDiary_FINAL_T1Data_updated1.10.26.xlsx"))

diary_t2 <- readxl::read_xlsx(here("Period_Pain/Data", "E-Sleep_DailyDiary_FINAL_T2Data_updated1.10.26.xlsx"))
```

```{r, include = FALSE}
actigraphy_t1_dec <- actigraphy_t1 %>% 
  select(-start_time_t1, -end_time_t1) %>% 
  mutate(subject_id_t1 = as.double(subject_id_t1))

actigraphy_t1_dec <- actigraphy_t1_dec %>% 
  mutate(subject_id_t1 = case_when(
    # Subject 524 became NA after changing it to a double
    is.na(subject_id_t1) ~ 524,
    TRUE ~ subject_id_t1
  ))

actigraphy_t2_dec <- actigraphy_t2 %>% 
  select(-start_time_t2, -end_time_t2) %>% 
  mutate(subject_id_t2 = as.double(subject_id_t2))

diary_t1$T1_DD_NightDate = as.Date(diary_t1$T1_DD_NightDate, origin = "1899-12-30")
diary_t2$T2_DD_NightDate = as.Date(diary_t2$T2_DD_NightDate, origin = "1899-12-30")

t1_joined <- diary_t1 %>% 
  full_join(actigraphy_t1_dec, by = c("C_ID" = "subject_id_t1", "T1_DD_DD_Interval" = "interval_number_t1"))

t2_joined <- diary_t2 %>% 
  full_join(actigraphy_t2_dec, by = c("C_ID" = "subject_id_t2", "T2_DD__DD_Interval" = "interval_number_t2"))

names(t1_joined) <- gsub("T1", "T", names(t1_joined))
names(t1_joined) <- gsub("t1", "T", names(t1_joined))
t1_joined
names(t2_joined) <- gsub("T2", "T", names(t2_joined))
names(t2_joined) <- gsub("t2", "T", names(t2_joined))
t2_joined

setdiff(names(t1_joined), names(t2_joined))
setdiff(names(t2_joined), names(t1_joined))

t2 <- t2_joined %>%
  rename(T_DD_DD_Interval = T_DD__DD_Interval,
         T_DD_NapDuration = "T_DD_-NapDuration",
         T_DD_CaffType_Juice = T_DD_CaffType_Juices,
         T_DD_MedType3_SSRIs = T_DD_Medtype3_SSRIs,
         onset_latency_T = onset_latency_T...9,
         sleep_midpoint_T = "sleep midpoint_T") %>% 
  select(-onset_latency_T...10)

t1 <- t1_joined %>% 
  rename(T_DD_CaffAmt_LessThanTheRecommendedAmt = T_DD_CaffAmt_LessThanTheRecommendedAmount,
         T_DD_CaffAmt_TheRecommendedAmt = T_DD_CaffAmt_TheRecommendedAmount,
         T_DD_CaffAmt_GreaterThanTheRecommendedAmt = T_DD_CaffAmt_GreaterThanTheRecommendedAmount)

setdiff(names(t2), names(t1))
setdiff(names(t1), names(t2)) # Everything in t1 is present in t2, but MedType6 is not present in t1. 

# TO DO...
# 1) Make sure all variables are of the same class between the t1 and t2 datasets
# 2) Figure out what to do with MedType6 (exists in t2 and not t1)
# 3) Change all -999 variables to NA (done)
# 4) Update DayType using NightDate to be school night or not school night (done)
t1 %>% 
  filter(T_DD_Period == 1) %>% 
  select(C_ID, T_DD_Period, T_DD_PeriodPain, T_DD_PeriodDay) %>%
  group_by(C_ID) %>% 
  summarise(num_days = n_distinct(T_DD_PeriodDay))
 
t2 %>% 
  filter(T_DD_Period == 1) %>% 
  select(C_ID, T_DD_Period, T_DD_PeriodPain, T_DD_PeriodDay) %>%
  group_by(C_ID) %>% 
  summarise(num_days = n_distinct(T_DD_PeriodDay))

#Replacing 999 with NAs in t1 and t2
t1[t1==-999] = NA
t1[t1==-99] = NA
t1  
t2[t2==-999] = NA
t2[t2==-99] = NA

#glimpse(t1)
#glimpse(t2)

#Update DayType to 1 is friday-saturday and 0 is any other night
## This doesn't work. T_DD_NightDate isn't stored as a datetime variable in the data after it's
## read into R. Furthermore, the model sheet asks for a school day or off day. That's a variable 
## already present in this dataset with 0 or 1.
t1 <- t1 %>% mutate(weekend = ifelse((wday(T_DD_NightDate, label = TRUE)) %in% c("Fri","Sat"),1,0))
t2 <- t2 %>% mutate(weekend = ifelse((wday(T_DD_NightDate, label = TRUE)) %in% c("Fri","Sat"),1,0))

#Binding the times into one dataset

#create a variable for checking for painkiller (ibuprofen, tylenol)
table(t1$T_DD_MedType1)

table(t2$T_DD_MedType6)
table(t2$T_DD_MedType1)

#Add painkiller indicator
t1 <- t1 %>% mutate(painkiller = ifelse(T_DD_MedType1 %in% c("advil","ibuprofen","Ibuprofen","Ibuprofin"),1,0))
t2 <- t2 %>% mutate(painkiller = ifelse(T_DD_MedType1 %in% c("advil","Advil","ibuprofen","Ibuprofen","Ibuprofin","tylenol") |
                                        T_DD_MedType2 %in% c("advil","Advil","ibuprofen","Ibuprofen","Ibuprofin","tylenol") |
                                        T_DD_MedType6 %in% c("advil","Advil","ibuprofen","Ibuprofen","Ibuprofin","tylenol"),1,0))

#Add time variable
t1 <- t1 %>% mutate(Time = 0, 
                    T_DD_NapOnset = as.numeric(T_DD_NapOnset),
                    T_DD_NapDuration = as.numeric(T_DD_NapDuration),
                    T_DD_ActiDur = as.numeric(T_DD_ActiDur),
                    T_DD_SleepyAlert = as.numeric(T_DD_SleepyAlert),
                    T_DD_MorningDate = as.numeric(T_DD_MorningDate))
t2 <- t2 %>% mutate(Time = 1, 
                    T_DD_NapOnset = as.numeric(T_DD_NapOnset),
                    T_DD_NapDuration = as.numeric(T_DD_NapDuration),
                    T_DD_SleepyAlert = as.numeric(T_DD_SleepyAlert),
                    T_DD_MorningDate = as.numeric(T_DD_MorningDate))

t1 <- t1 %>% select(-c(T_DD_MedType1:T_DD_MedTime5))
t2 <- t2 %>% select(-c(T_DD_MedType1:T_DD_MedTime6))

t1 <- t1 %>% left_join(Empathy %>% select(C_ID, demo_child_age_check_t1:weight3t1, BodyTotalt1), by = "C_ID")
names(t1)[grepl("t1",names(t1))] <- gsub("_t1","",names(t1)[grepl("t1",names(t1))])
names(t1)[grepl("t1",names(t1))] <- gsub("t1","",names(t1)[grepl("t1",names(t1))])

t2 <- t2 %>% left_join(Empathy %>% select(C_ID, demo_child_age_check_t2:weightdifft2, BodyTotalt2), by = "C_ID")
names(t2)[grepl("t2",names(t2))] <- gsub("_t2","",names(t2)[grepl("t2",names(t2))])
names(t2)[grepl("t2",names(t2))] <- gsub("t2","",names(t2)[grepl("t2",names(t2))])
names(t2)[names(t2) == "weigh"] <- "weight2"

# Have to remove weight3 from t1, completely full of NAs after the above operations
t1 <- t1 %>% select(-weight3)

# BodyTotal was stored as a character in t2, as was BMI
t2$BMI <- as.numeric(t2$BMI)
t2$BodyTotal <- as.numeric(t2$BodyTotal)
sleepfull <- bind_rows(t1, t2)

# sleepfull <- sleepfull %>% left_join(Empathy %>% select(C_ID,BodyTotalt0) %>% mutate(BodyTotalt0 = as.numeric(BodyTotalt0)), by = "C_ID")

# rename age and change age and BMI to numeric
sleepfull <- sleepfull %>% mutate(demo_child_age_check = as.numeric(demo_child_age_check)) %>% rename(age = demo_child_age_check)
sleepfull <- sleepfull %>% mutate(BMI = as.numeric(BMI)) 

sleepfull %>% filter(C_ID == 442) %>% select(C_ID, T_DD_NightDate,T_DD_Period, T_DD_PeriodFlow, T_DD_PeriodPain)
table(sleepfull$demo_degree)
table(sleepfull$T_DD_PeriodPain,sleepfull$T_DD_Period)
table(sleepfull$T_DD_PeriodPain)
table(sleepfull$T_DD_PeriodFlow)
```


# EDA

```{r}
#How many unique people are there at each time point. 
#How many days is someone on their period. 
#How many are ever on their periods

table(sleepfull$T_DD_Period)
89/(538+89+1)
table(sleepfull$T_DD_Period, sleepfull$Time)
49/(374+49+1)
40/(164+40)

#How many days on period at time 1 and time 2.  
sleepfull %>% group_by(Time, T_DD_Period) %>% summarize(n = n())

sleepfull %>% group_by(Time, T_DD_Period) %>% summarize(mn = mean(T_DD_PeriodPain, na.rm = T), n = n())

#Person 404 is reporting period pain and flow at time 2 but period is 0. FIXED IN RAW DATA
sleepfull %>% filter(T_DD_Period == 0 & Time == 0 ) %>% select(C_ID, T_DD_Period,T_DD_PeriodDay, T_DD_PeriodPain, T_DD_PeriodFlow)
sleepfull %>% filter(T_DD_Period == 0 & Time == 1 ) %>% select(C_ID, T_DD_Period,T_DD_PeriodDay, T_DD_PeriodPain, T_DD_PeriodFlow) 
sleepfull %>% filter(T_DD_Period == 0 & Time == 2 ) %>% select(C_ID, T_DD_Period,T_DD_PeriodDay, T_DD_PeriodPain, T_DD_PeriodFlow) 

sleepfull %>% filter(C_ID == 404) %>% select(C_ID, T_DD_NightDate, T_DD_Period, T_DD_PeriodDay, T_DD_PeriodPain, T_DD_PeriodFlow) 
#table(sleepfull$T_DD_PeriodFlow)
#table(sleepfull$T_DD_PeriodPain)


sleepfull %>% group_by(Time) %>% summarise(mn = mean(painkiller), n = n(), sum(painkiller))

#How much is missing?
apply(sleepfull, 2, function(x){sum(is.na(x))})

ggplot(aes(x = T_DD_PeriodPain, y = sleep_time_T, color = as.factor(T_DD_Period)), data = sleepfull) + geom_point() + geom_smooth()
ggplot(aes(x = T_DD_PeriodFlow, y = sleep_time_T, color = as.factor(T_DD_Period)), data = sleepfull) + geom_point() + geom_smooth()

ggplot(aes(x = T_DD_PeriodPain, y = end_time_dec_T, color = as.factor(T_DD_Period)), data = sleepfull) + geom_point() + geom_smooth()
ggplot(aes(x = T_DD_PeriodFlow, y = end_time_dec_T, color = as.factor(T_DD_Period)), data = sleepfull) + geom_point() + geom_smooth()

ggplot(aes(x = T_DD_PeriodPain, y = start_time_TRM_T, color = as.factor(T_DD_Period)), data = sleepfull) + geom_point() + geom_smooth()
ggplot(aes(x = T_DD_PeriodFlow, y = start_time_TRM_T, color = as.factor(T_DD_Period)), data = sleepfull) + geom_point() + geom_smooth()

ggplot(aes(x = T_DD_PeriodPain, y = efficiency_T, color = as.factor(T_DD_Period)), data = sleepfull) + geom_point() + geom_smooth()
ggplot(aes(x = T_DD_PeriodFlow, y = efficiency_T, color = as.factor(T_DD_Period)), data = sleepfull) + geom_point() + geom_smooth()

ggplot(aes(x = T_DD_PeriodPain, y = log(waso_T+ 1), color = as.factor(T_DD_Period)), data = sleepfull) + geom_point() + geom_smooth()
ggplot(aes(x = T_DD_PeriodFlow, y = log(waso_T+ 1), color = as.factor(T_DD_Period)), data = sleepfull) + geom_point() + geom_smooth()

ggplot(aes(x = T_DD_PeriodPain, y = log(waso_T + 1), color = as.factor(Time)), data = sleepfull) + geom_point() + geom_smooth()
ggplot(aes(x = T_DD_PeriodFlow, y = log(waso_T + 1), color = as.factor(Time)), data = sleepfull) + geom_point() + geom_smooth()
```


# Josie and Oliver Preliminary Models

```{r}
# no interaction terms between period and pain/flow
# kept interaction term between age and time

## TO DO:
## 1. need to add painkiller to models

## OLIVER NOTES:
## We should remove age:time and time from the models at time 0 and time 1
## because Time will be constant in these models. 

############################
#Duration sleep_time_1
############################

## PAIN
mod_sleep_time_all <- lmer(sleep_time_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) * Time + T_DD_PeriodPain + (1|C_ID), data = sleepfull)
summary(mod_sleep_time_all)

mod_sleep_time_0 <- lmer(sleep_time_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodPain + (1|C_ID), data = sleepfull %>% filter(Time == 0))
summary(mod_sleep_time_0)

mod_sleep_time_1 <- lmer(sleep_time_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodPain + (1|C_ID), data = sleepfull %>% filter(Time == 1))
summary(mod_sleep_time_1)


## FLOW
mod_sleep_time_all <- lmer(sleep_time_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) * Time + T_DD_PeriodFlow + (1|C_ID), data = sleepfull)
summary(mod_sleep_time_all)

mod_sleep_time_0 <- lmer(sleep_time_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodFlow + (1|C_ID), data = sleepfull %>% filter(Time == 0))
summary(mod_sleep_time_0)

mod_sleep_time_1 <- lmer(sleep_time_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodFlow + (1|C_ID), data = sleepfull %>% filter(Time == 1))
summary(mod_sleep_time_1)


############################
#Offset/Waketime (end_time_dec_t2)
############################

#C_ID 494 is waking up at like 10pm?
ggplot(aes(x = end_time_dec_T), data = sleepfull) + geom_histogram()
sleepfull %>% filter(end_time_dec_T > 20)

sleepfull$end_time_dec_T[!is.na(sleepfull$end_time_dec_T) & sleepfull$end_time_dec_T > 20] <- sleepfull$end_time_dec_T[!is.na(sleepfull$end_time_dec_T) & sleepfull$end_time_dec_T > 20] - 24

## PAIN

mod_offset_all <- lmer(end_time_dec_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) * Time + T_DD_PeriodPain + (1|C_ID), data = sleepfull)
summary(mod_offset_all)

mod_offset_0 <- lmer(end_time_dec_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodPain + (1|C_ID), data = sleepfull %>% filter(Time == 0))
summary(mod_offset_0)

mod_offset_1 <- lmer(end_time_dec_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodPain + (1|C_ID), data = sleepfull %>% filter(Time == 1))
summary(mod_offset_1)


## FLOW

mod_offset_all <- lmer(end_time_dec_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) * Time + T_DD_PeriodFlow + (1|C_ID), data = sleepfull)
summary(mod_offset_all)

mod_offset_0 <- lmer(end_time_dec_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodFlow + (1|C_ID), data = sleepfull %>% filter(Time == 0))
summary(mod_offset_0)

mod_offset_1 <- lmer(end_time_dec_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodFlow + (1|C_ID), data = sleepfull %>% filter(Time == 1))
summary(mod_offset_1)


############################
#Onset/Falling Asleep (start_time_TRM_t2)
############################

## PAIN

mod_onset_all <- lmer(start_time_TRM_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) * Time + T_DD_PeriodPain + (1|C_ID), data = sleepfull)
summary(mod_onset_all)
plot(mod_onset_all)

mod_onset_0 <- lmer(start_time_TRM_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodPain + (1|C_ID), data = sleepfull %>% filter(Time == 0))
summary(mod_onset_0)

mod_onset_1 <- lmer(start_time_TRM_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodPain + (1|C_ID), data = sleepfull %>% filter(Time == 1))
summary(mod_onset_1)


## FLOW

mod_onset_all <- lmer(start_time_TRM_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) * Time + T_DD_PeriodFlow + (1|C_ID), data = sleepfull)
summary(mod_onset_all)
plot(mod_onset_all)

mod_onset_0 <- lmer(start_time_TRM_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodFlow + (1|C_ID), data = sleepfull %>% filter(Time == 0))
summary(mod_onset_0)

mod_onset_1 <- lmer(start_time_TRM_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodFlow + (1|C_ID), data = sleepfull %>% filter(Time == 1))
summary(mod_onset_1)


############################
#Efficiency (efficiency_t2)
############################

## PAIN

mod_eff_all <- lmer(efficiency_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) * Time + T_DD_PeriodPain + (1|C_ID), data = sleepfull)
summary(mod_eff_all)
plot(mod_eff_all)

mod_eff_0 <- lmer(efficiency_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodPain + (1|C_ID), data = sleepfull %>% filter(Time == 0))
summary(mod_eff_0)

mod_eff_1 <- lmer(efficiency_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodPain + (1|C_ID), data = sleepfull %>% filter(Time == 1))
summary(mod_eff_1)


## FLOW

mod_eff_all <- lmer(efficiency_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) * Time + T_DD_PeriodFlow + (1|C_ID), data = sleepfull)
summary(mod_eff_all)
plot(mod_eff_all)

mod_eff_0 <- lmer(efficiency_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodFlow + (1|C_ID), data = sleepfull %>% filter(Time == 0))
summary(mod_eff_0)

mod_eff_1 <- lmer(efficiency_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodFlow + (1|C_ID), data = sleepfull %>% filter(Time == 1))
summary(mod_eff_1)


############################
#Awakenings (waso_t2)
############################

hist(sleepfull$waso_T) # might need log

## PAIN

mod_waso_all <- lmer(waso_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) * Time + T_DD_PeriodPain + (1|C_ID), data = sleepfull)
summary(mod_waso_all)
plot(mod_waso_all)

mod_waso_0 <- lmer(waso_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodPain + (1|C_ID), data = sleepfull %>% filter(Time == 0))
summary(mod_waso_0)

mod_waso_1 <- lmer(waso_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodPain + (1|C_ID), data = sleepfull %>% filter(Time == 1))
summary(mod_waso_1)


## FLOW

mod_waso_all <- lmer(waso_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) * Time + T_DD_PeriodFlow + (1|C_ID), data = sleepfull)
summary(mod_waso_all)
plot(mod_waso_all)

mod_waso_0 <- lmer(waso_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodFlow + (1|C_ID), data = sleepfull %>% filter(Time == 0))
summary(mod_waso_0)

mod_waso_1 <- lmer(waso_T ~ 1 + BodyTotal + weekend + T_DD_Period + BMI + I(age-13) + T_DD_PeriodFlow + (1|C_ID), data = sleepfull %>% filter(Time == 1))
summary(mod_waso_1)

pairs(sleepfull %>% select(BodyTotal, weekend, T_DD_Period, BMI, age, T_DD_PeriodFlow))
```
